---
title: "Bootstrap App"
author: "Alexandre Hild Aono - 92169<br>Ricardo Manhães Savii - 92482"
date: "5 de Outubro de 2016"
output: 
  ioslides_presentation: 
    fig_caption: yes
    css: presentation_custom.css
    logo: unifesp-logo-branco.png
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Shiny Presentation {#apresentacao}

This R Markdown presentation is made interactive using Shiny. The viewers of the presentation can change the assumptions underlying what's presented and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

Sugiro este link também: [formatando apresetações](http://rmarkdown.rstudio.com/ioslides_presentation_format.html)

## Interactive Plot

```{r eruptions}

```

## Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Python Output

```{python}
for i in range(1,10):
  print "Hello World!" + str(i)
```



## Bootstrap App

### <strong>Obrigado!</strong>

> Alexandre Hild Aono (92169)

> Ricardo Manhães Savii (92482)
